\fred{A Unified Treatment of Tractabilty of Approximation Problems}\\ \peter{[PETER: In view of the papers of Henryk and Michael, maybe we should think of a better title?]}

### 2023-06-20 GeneralizedTractability_230607.tex
Updates from Overleaf

\Cref{thm_main_strong_tract2,thm_main_tract2,thm_main_rest_strong_tract,thm_main_rest_tract} all take the form
\begin{multline}
  \exists C_{\vp} \text{ with }
    \comp(\varepsilon, d) \le  C_{\vp}\, T(\varepsilon^{-1},\clubsuit,\vp) \quad \forall (\varepsilon^{-1},d) \in \Omega \\
    \iff   \exists L_{\vp} \text{ with }
    \sup_{d \in \naturals}
     \sum_{i = \lceil L_{\vp}\, T(0,\clubsuit,\vp) \rceil}^{\spadesuit(d)} \frac{1}{T(\lambda^{-1}_{i,d},\clubsuit,\vp)}< \infty, \\
     \clubsuit \in \{1,d\}, \ \varheartsuit(d) = \inf \{\varepsilon : (\varepsilon^{-1},d) \in \Omega \}, \ 
     \spadesuit(d) = \begin{cases}
        \min\{n \in \natzero : \lambda_{n+1,d} \le \varheartsuit(d) \}, &   \varheartsuit(d)< 0, \\
        \infty, & \varheartsuit(d) = 0.
        \end{cases}
\end{multline}
\Cref{thm:subhT} is of similar, but not equivalent, form.

@@

For this definition of tractability to make sense we assume that
\begin{subequations} \label{eq:Tconditions}
\begin{equation} \label{eq:Tnondecreasing}
	T \text{ is non-decreasing in all variables,}
\end{equation}
which implies that the problem is expected to be no easier by decreasing the tolerance, $\varepsilon$, or increasing the dimension, $d$. Furthermore, increasing $\vp$ does not decrease $T(\cdot, \cdot, \vp)$.  Since there are an infinite number of positive eigenvalues, it also makes sense to assume that
\begin{equation}
	\lim_{\varepsilon \to 0} T(\varepsilon^{-1},d,\vp) = \infty \qquad \forall d \in \naturals, \ \vp \in [0,\infty)^s.
\end{equation}
Since $T(\cdot,d,\vp)$ is non-decreasing, we may define the following limit, which we assume will always be positive:
\begin{equation}\label{eq:T0}	T(0,d,\vp):=\lim_{\varepsilon\to\infty}T(\varepsilon^{-1},d,\vp) \ge T(0,1,\vzero) > 0.
\end{equation}
\end{subequations}
Finally, there is a technical assumption required for our analysis.  There exists a $K_{\vp,\tau}$ depending on $\vp$ and $\tau$, but  independent of $\varepsilon$ and $d$, such that
\begin{equation} \label{eq:ptauassume}
	[T(\varepsilon^{-1},d,\vp)]^\tau \le K_{\vp,\tau} T(\varepsilon^{-1},d,\tau \vp),   \quad \forall \varepsilon \in (0,\infty), \ d \in \naturals, \ \vp\in[0,\infty)^s, \ \tau\in [1,\infty).
\end{equation}

@@

\section{Examples} \label{sec:examples}
%In this section, we illustrate Theorems \ref{thm_main_strong_tract2} and \ref{thm_main_tract2} for the types of tractability given in the table in Section \ref{sec:not}.
In this section, we present six examples related to Theorem \ref{thm_main_strong_tract2} and Theorem \ref{thm_main_tract2} introduced in Section \ref{sec:spt}. We will continue to present examples in later sections.

In Section 2.2 we considered strong tractability. 
\begin{example}[Strong algebraic polynomial tractability]

@@

\begin{example}[Strong exponential polynomial tractability]
Let the tractability function, $T$,
be defined by
\[
 T(\varepsilon^{-1},d,\vp)= \left[\max\{1,\log(1+\varepsilon^{-1})\}\right]^p, \quad \forall \varepsilon > 0, \,  d \in \naturals, \, \vp \in [0,\infty),
\]
where $\vp$ is a scalar. Then Theorem \ref{thm_main_strong_tract2} yields the equivalent condition for strong exponential polynomial tractability \[
 \sup_{d\in\naturals} \sum_{i=L_{p} }^\infty (\min\{1,\log(1+\lambda_{i,d}\})^{p}  < \infty,\quad  \text{ for some } p \ge 0, L_{p} \in \naturals
\] In this case the optimal $p$ is the infimum of all $p$ for which the above condition holds.
\end{example}
\begin{example}[Exponential polynomial tractability]
Let the tractability function, $T$,
be defined by
\[
 T(\varepsilon^{-1},d,\vp)=\left[\max\{1,\log(1+\varepsilon^{-1}\})\right]^p\, d^q, \qquad \forall \varepsilon > 0, \,  d \in \naturals, \, \vp \in [0,\infty)^2, 
\] where $\vp = (p,q)$. Then Theorem \ref{thm_main_tract2} yields  the equivalent condition for exponential polynomial tractability
\[
 \sup_{d\in\naturals}\, d^{-q} \sum_{i=\lceil L_{(p,q)} d^{q}\rceil}^\infty [\min\{1,\log(1+\lambda_{i,d}\})]^p < \infty  \text{ for some } p,q \ge 0, L_{(p,q)} \in \naturals.
\]
\end{example}

\begin{example}[(Strong) Separable tractability]
Suppose that the tractability function is defined by
\[
 T(\varepsilon^{-1},d,\vp)= \phi(\varepsilon^{-1},p)\, \psi(d,q)
 \qquad \forall \varepsilon > 0, \,  d \in \naturals, \, \vp \in [0,\infty)^2.
\]
with non-decreasing functions $\phi : (0,\infty) \times (0,\infty) \to (0,\infty)$ and $\psi : \naturals  \times (0,\infty) \to (0,\infty)$ and where $\vp = (p,q)$, hence $T$ is non-decreasing in all variables.

>>>>

\Cref{thm_main_strong_tract2,thm_main_tract2,thm_main_rest_strong_tract,thm_main_rest_tract} all take the form
\begin{multline}
  \exists C_{\vp} \text{ with }
    \comp(\varepsilon, d) \le  C_{\vp}\, T(\varepsilon^{-1},\clubsuit,\vp) \quad \forall (\varepsilon^{-1},d) \in \Omega \\
    \iff   \exists L_{\vp} \text{ with }
    \sup_{d \in \naturals}
     \sum_{i = \lceil L_{\vp}\, T(0,\clubsuit,\vp) \rceil}^{\spadesuit(d)} \frac{1}{T(\lambda^{-1}_{i,d},\clubsuit,\vp)}< \infty, \\
     \clubsuit \in \{1,d\}, \ \varheartsuit(d) := \inf \{\varepsilon : (\varepsilon^{-1},d) \in \Omega \}, \ 
     \spadesuit(d) := \begin{cases}
        \min\{n \in \natzero : \lambda_{n+1,d} \le \varheartsuit(d) \}, &   \varheartsuit(d) > 0, \\
        \infty, & \varheartsuit(d) = 0.
        \end{cases}
\end{multline}
\Cref{thm:subhT} is of similar, but not equivalent, form.

@@

For this definition of tractability to make sense we assume that
\begin{subequations} \label{eq:Tconditions}
\begin{equation} \label{eq:Tnondecreasing}
	T \text{ is non-decreasing in all variables,}
\end{equation}
which implies that the problem is expected to be no easier by decreasing the tolerance, $\varepsilon$, or increasing the dimension, $d$. (This is why we make $T$ a function of $\varepsilon^{-1}$ rather than of $\varepsilon$.) Furthermore, increasing $\vp$ does not decrease $T(\cdot, \cdot, \vp)$.  Since there are an infinite number of positive eigenvalues, it also makes sense to assume that
\begin{equation}
	\lim_{\varepsilon \to 0} T(\varepsilon^{-1},d,\vp) = \infty \qquad \forall d \in \naturals, \ \vp \in [0,\infty)^s.
\end{equation}
Since $T(\cdot,d,\vp)$ is non-decreasing, we may define the following limit, which we assume will always be positive:
\begin{equation}\label{eq:T0}	T(0,d,\vp):=\lim_{\varepsilon\to\infty}T(\varepsilon^{-1},d,\vp) = \inf_\varepsilon T(\varepsilon^{-1},d,\vp) \ge T(0,1,\vzero) > 0.
\end{equation}
\end{subequations}
Finally, there is a technical assumption required for our analysis.  There exists a $K_{\vp,\tau}$ depending on $\vp$ and $\tau$, but  independent of $\varepsilon$ and $d$, such that
\begin{equation} \label{eq:ptauassume}
	[T(\varepsilon^{-1},d,\vp)]^\tau \le K_{\vp,\tau} T(\varepsilon^{-1},d,\tau \vp),   \quad \forall \varepsilon \in (0,\infty), \ d \in \naturals, \ \vp\in[0,\infty)^s, \ \tau\in [1,\infty).
\end{equation}

@@

\section{Examples} \label{sec:examples}
%In this section, we illustrate Theorems \ref{thm_main_strong_tract2} and \ref{thm_main_tract2} for the types of tractability given in the table in Section \ref{sec:not}.
In this section, we present six examples relating to Theorem \ref{thm_main_strong_tract2} and Theorem \ref{thm_main_tract2}, both of which were introduced in Section \ref{sec:spt}, for the various types of tractability that are listed in Table \ref{tab:commonT}. In subsequent sections, we will continue to present various examples.

%In this section, we present six examples related to Theorem \ref{thm_main_strong_tract2} and Theorem  introduced in Section \ref{sec:spt} where the types of tractability were given in the table. We will continue to present examples in later sections.

The (strong) polynomial tractability for both the algebraic case and the exponential case will be first considered as follows: 
\begin{example}[Strong algebraic polynomial tractability]

@@

\begin{example}[Strong exponential polynomial tractability]
Let the tractability function, $T$,
be defined by
\[
 T(\varepsilon^{-1},d,\vp)= \left[\max\{1,\log(1+\varepsilon^{-1})\}\right]^p, \quad \forall \varepsilon > 0, \,  d \in \naturals, \, \vp \in [0,\infty),
\]
where $\vp$ is a scalar. Then Theorem \ref{thm_main_strong_tract2} yields the equivalent condition for strong exponential polynomial tractability \[
 \sup_{d\in\naturals} \sum_{i=L_{p} }^\infty (\min\{1,\log(1+\lambda_{i,d}\})^{p}  < \infty,\quad  \text{ for some } p \ge 0, L_{p} \in \naturals
\] In this case the optimal $p$ is the infimum of all $p$ for which the above condition holds.
\end{example}
\begin{example}[Exponential polynomial tractability]
Let the tractability function, $T$,
be defined by
\[
 T(\varepsilon^{-1},d,\vp)=\left[\max\{1,\log(1+\varepsilon^{-1}\})\right]^p\, d^q, \qquad \forall \varepsilon > 0, \,  d \in \naturals, \, \vp \in [0,\infty)^2, 
\] where $\vp = (p,q)$. Then Theorem \ref{thm_main_tract2} yields  the equivalent condition for exponential polynomial tractability
\[
 \sup_{d\in\naturals}\, d^{-q} \sum_{i=\lceil L_{(p,q)} d^{q}\rceil}^\infty [\min\{1,\log(1+\lambda_{i,d}\})]^p < \infty  \text{ for some } p,q \ge 0, L_{(p,q)} \in \naturals.
\]
\end{example}
We summarize the tractability notions in the previous examples in the following example. The
\begin{example}[(Strong) Separable tractability]
Suppose that the tractability function is defined by
\[
 T(\varepsilon^{-1},d,\vp)= \phi(\varepsilon^{-1},p)\, \psi(d,q)
 \qquad \forall \varepsilon > 0, \,  d \in \naturals, \, \vp \in [0,\infty)^2.
\]
with non-decreasing functions $\phi : (0,\infty) \times (0,\infty) \to (0,\infty)$ and $\psi : \naturals  \times (0,\infty) \to (0,\infty)$ and where $\vp = (p,q)$, hence $T$ is non-decreasing in all variables.
